Supplement for: Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-11-12 manuscripts/supplement.Rmd
rebuild final data files for uploading

While the data can be regenerated using the code provided, for convenience
CSV files of the data shown in each graph are made available on Dryad.

@@

@@

```{r figure_S2, fig.height=6, fig.width=6, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histograms shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values of 1 indicate optimal performance. Columns indicate different models, rows different noise levels, and colors indicate the parameter set used. Grouped over stochastic replicates applying the contol policy and stochastic replicates of training data generated from the model indicated, see raw data for details. Randomly chosen parameter values for the models shown in tables below."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=parameters)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/figureS2.csv") 
```

@@

```{r figure_S4, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red.", fig.width=4, fig.height=4}
gp_assessment_plots$posteriors_plot
write.csv(gp_dat,"components/data/figureS3-4.csv")
```

@@

```{r figure_S5, fig.height=6, fig.cap="Traces from the MCMC estimates of the Ricker model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=4}
ggplot(ricker_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S6, fig.cap="Posteriors from the MCMC estimate of the Ricker model", fig.width=4, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(ricker_posteriors, "components/data/figureS5-6.csv")
```

@@

```{r figure_S7, fig.height=6, fig.cap="Traces from the MCMC estimates of the Myers model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=4}
ggplot(myers_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S8, fig.cap="Posterior distributions from the MCMC estimates of the Myers model", fig.width=4, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(myers_posteriors, "components/data/figureS7-8.csv")
```

@@

```{r figure_S9, fig.height=6, fig.cap="Traces from the MCMC estimates of the Allen model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps)", fig.width=4}
ggplot(allen_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S10, fig.cap="Posteriors from the MCMC estimate of the Allen model", fig.width=4, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(allen_posteriors, "components/data/figureS9-10.csv")
```

>>>>

While the data can be regenerated using the code provided, for convenience
CSV files of the data shown in each graph are made available on Dryad,
along with the source `.Rmd` files for the manuscript and supplement
that document them.

@@

```{r S1_eml, eval=FALSE}
## Forgo the EML generation, the Rmd files provide better documentation at this stage.
library(EML)
me <- "Carl Boettiger <cboettig@ropensci.org>"
models <- levels(crash_data$variable)
names(models) <- models
col.defs <- c("time", "fish stock", "model", "value", "replicate")
unit.defs <- list("number", "number", models, "number", "number")
col.classes <- sapply(crash_data, class)
eml_write("components/data/figureS1.csv", col.classes = col.classes, col.defs=col.defs,unit.defs=unit.defs,creator=me, title="Figure S1", file="components/data/README_S1.xml")
```

@@

```{r figure_S2, fig.height=6, fig.width=6, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histograms shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values of 1 indicate optimal performance. Columns indicate different models, rows different noise levels, and colors indicate the parameter set used. Grouped over stochastic replicates applying the contol policy and stochastic replicates of training data generated from the model indicated, see raw data for details. Randomly chosen parameter values for the models shown in tables below."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=parameters)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/figureS2.csv") 
```
```{r S2_eml, eval=FALSE}
# not descriptive enough, supplement text documents this better
par <- levels(sensitivity_dat$parameters)
names(par) <- par
col.defs <- names(sensitivity_dat)
unit.defs <- list(models, par, "number", "number",  "number", "number")
col.classes <- sapply(sensitivity_dat, class)
eml_write("components/data/figureS2.csv", col.classes = col.classes, col.defs=col.defs,unit.defs=unit.defs,creator=me, title="Figure S2", file="components/data/README_S2.xml")
```

@@

```{r figure_S4, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red; note the posterior distributions are significantly more peaked than the priors, showing that the data has been informative and is not driven by the priors.", fig.width=4, fig.height=4}
gp_assessment_plots$posteriors_plot
write.csv(tgp_dat,"components/data/figureS3-4.csv")
```

```{r S2_eml}
par <- levels(sensitivity_dat$parameters)
names(par) <- par
col.defs <- names(sensitivity_dat)
unit.defs <- list(models, par, "number", "number",  "number", "number")
col.classes <- sapply(sensitivity_dat, class)
eml_write("components/data/figureS2.csv", col.classes = col.classes, col.defs=col.defs,unit.defs=unit.defs,creator=me, title="Figure S2", file="components/data/README_S2.xml")
```

@@

```{r figure_S5, fig.height=6, fig.cap="Traces from the MCMC estimates of the Ricker model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps). stdQ refers to the estimate of $\\sigma$; deviance is -2 times the log likelihood. ", fig.width=4}
ggplot(ricker_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S6, fig.cap="Posteriors from the MCMC estimate of the Ricker model. Note that the model estimates a carrying capacity $K$ very close to the true equilibrium where most of the observations were made, but is less certain about the growth rate.", fig.width=4, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(ricker_posteriors, "components/data/figureS5-6.csv")
```

@@

```{r figure_S7, fig.height=6, fig.cap="Traces from the MCMC estimates of the Myers model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps). stdQ refers to the estimate of $\\sigma$; deviance is -2 times the log likelihood.", fig.width=4}
ggplot(myers_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S8, fig.cap="Posterior distributions from the MCMC estimates of the Myers model. Note that with more free parameters, the posteriors reflect greater uncertainty.  In particular, the parameter $\\theta$ includes values both above 2, resulting in a tipping point, and below 2, where no tipping point exists in the model.  Though the dynamic program will integrate over the full distribution, including those values corresponding to tipping points, the weight of the model lies in the region without tipping points.", fig.width=4, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(myers_posteriors, "components/data/figureS7-8.csv")
```

@@

```{r figure_S9, fig.height=6, fig.cap="Traces from the MCMC estimates of the Allen model show reasonable mixing (no trend) and sampling rejection rate (no piecewise jumps). stdQ refers to the estimate of $\\sigma$; deviance is -2 times the log likelihood.", fig.width=4}
ggplot(allen_posteriors) + 
  geom_line(aes(index, value)) + # priors, need to fix order though
  facet_wrap(~ variable, scale="free_y", ncol=1)
```

```{r figure_S10, fig.cap="Posteriors from the MCMC estimate of the Allen model. The Allen model is the structurally correct model.  Despite potential identfiability issues in distinguishing between the stable and unstable points ($K$ and $\\theta$ respectively), the posterior estimates successfully reflect both the the upper stable point ($K$), as well as the significant probabilty of a tipping point ($\\theta$) somewhere between $K$ and extinction (0).", fig.width=4, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(allen_posteriors, "components/data/figureS9-10.csv")
```
